### 2017-04-14 paper/evaluation.tex
pass on eval
commenting rq5

%% Column
%% ``Group'' indicates the test cost group (see
%% Figure~\ref{fig:rq1-barplot}), the

\begin{figure}[t!]
%\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
  %    \footnotesize
  \small
    \centering
%    \setlength{\tabcolsep}{2.5pt}
%    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{lrr}
        \toprule
        \emph{Subject} & \emph{\# of modules} & \emph{Mode}\\%
        \midrule%
        \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1/1 &  \ParClassSeqMeth{}\\%
        \Comment{Apache }Flink & 74/74 & \ForkSeq{} \\%        
        \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1/1 & \ForkSeq{}\\%
        \Comment{Spotify }Helios & 8/8 & \ForkSeq{}\\%
        Javaslang & 3/3 & \ParClassParMeth{}\\%
        Jcabi\Comment{ Github} & 1/1 & \ParClassParMeth{}\\%        
        \Comment{Hazelcast }Jet & 7/14 & \ForkSeq{}\\%
        \Comment{Apache Logging }Log4J2 & 25/31 & \ForkSeq{}\\%
        \Comment{Jankotek }MapDB & 1/2 & \ParClassParMeth{}\\%        
        \bottomrule%
    \end{tabular}
%    }
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
\end{figure}
%\end{wrapfigure}

@@

Considering question 2, the answers we collected show that six of the
\emailsProjectsAnswered{} projects execute tests in parallel.  This
mismatch is justified by cases where neither of our checks (static or
dynamic) could detect presence of parallelism.  A closer look at these
projects revealed that one of them contained a \emph{pom.xml} file
encapsulated in a jar file (similar case as reported in
Section~\ref{sec:rqC-2}), in one of the projects the particpant
considered that distributed CI was a form of parallelism, and in four
projects parallelism was implemented natively~---~two projects
implemented concurrency control with custom JUnit test runners and two
other projects implemented concurrency within test methods.  Note
that, considering four extra cases (ignored two distributed CI cases),
the usage of parallelization increases from \percentParallel{} to
\percentParallelUpdated{}.  However, we do not consider this change
significant enough to modify our conclusion about practical adoption
of parallelization (\numRQC{}).

@@

\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.18\textwidth]{plots/survey.pdf}
    \caption{\label{fig:rq5-answers}Summary of developer's answers to
      survey question~\ref{questionThree}.}
\end{wrapfigure}
Considering question 3, the distribution of answers was as follows.  A
total of \emailsA{} of the \emailsProjectsAnswered{} developers who
answered the survey did not know that parallelism was available in
Maven (option ``a''), \emailsB{} of developers mentioned that they did
not use parallelism concerned with possible concurrency issues (option
``b''), \emailsD{} of developers mentioned that continuous integration
services sufficed to provide timely feedback while running only smoke
tests (\ie{}, short-running tests) locally (option ``c'')\Comment{here
  I want to say that they use it for something like "non-blocking
  testing" while developing in a local machine}, and \emailsD{} of
developers who provided an alternative answer (option ``d'') mentioned
that using parallelism was not worth the effort of preparing the test
suites to take advantage of available processing power.  A total of
\emailsNA{} of participants did not answer the last question of the
survey.  Figure~\ref{fig:rq5-answers} shows a pie chart summarizing
the distribution of answers.

>>>>

%\begin{figure}[t!]
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
  \footnotesize
  %  \small
  \centering
  \setlength{\tabcolsep}{2.5pt}
%    \resizebox{.48\textwidth}{!}{%
    \begin{tabular}{lrr}
        \toprule
        \emph{Subject} & \emph{\# of modules} & \emph{Mode}\\%
        \midrule%
        \Comment{BounceStorage }Chaos\Comment{ HTTP Proxy} & 1/1 &  \ParClassSeqMeth{}\\%
        \Comment{Apache }Flink & 74/74 & \ForkSeq{} \\%        
        \Comment{JenkinsCI }Gerrit\Comment{ Trigger Plugin} & 1/1 & \ForkSeq{}\\%
        \Comment{Spotify }Helios & 8/8 & \ForkSeq{}\\%
        Javaslang & 3/3 & \ParClassParMeth{}\\%
        Jcabi\Comment{ Github} & 1/1 & \ParClassParMeth{}\\%        
        \Comment{Hazelcast }Jet & 7/14 & \ForkSeq{}\\%
        \Comment{Apache Logging }Log4J2 & 25/31 & \ForkSeq{}\\%
        \Comment{Jankotek }MapDB & 1/2 & \ParClassParMeth{}\\%        
        \bottomrule%
    \end{tabular}
%    }
    \caption{Subjects with parallel test execution enabled by
    default.}
    \label{tab:freqmodes-dynamic}
%\end{figure}
\end{wrapfigure}

@@

Considering question 2, the answers we collected show that six of the
\emailsProjectsAnswered{} projects execute tests in parallel.  This
mismatch is justified by cases where neither of our checks (static or
dynamic) could detect presence of parallelism.  A closer look at these
projects revealed that one of them contained a \emph{pom.xml} file
encapsulated in a jar file (similar case as reported in
Section~\ref{sec:rqC-2}), in one of the projects the particpant
considered that distributed CI was a form of parallelism, and in four
projects parallelism was implemented natively\Luis{$\leftarrow$ is
this the right word?}~---~two projects
implemented concurrency control with custom JUnit test runners and two
other projects implemented concurrency within test methods.  Note
that, considering four extra cases (ignored two distributed CI cases),
the usage of parallelization increases from \percentParallel{} to
\percentParallelUpdated{}.  However, we do not consider this change
significant enough to modify our conclusion about practical adoption
of parallelization (\numRQC{}).

@@

\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
    \centering
    \includegraphics[width=.18\textwidth]{plots/survey.pdf}
    \caption{\label{fig:rq5-answers}Summary of developer's answers to
      survey question~\ref{questionThree}.}
\end{wrapfigure}

Considering question 3, the distribution of answers was as follows.  A
total of \emailsA{} of the \emailsProjectsAnswered{} developers who
answered the survey did not know that parallelism was available in
Maven (option ``a''), \emailsB{} of developers mentioned that they did
not use parallelism concerned with possible concurrency issues (option
``b''), \emailsD{} of developers mentioned that continuous integration
services sufficed to provide timely feedback while running only smoke
tests (\ie{}, short-running tests) locally (option ``c'')\Comment{here
  I want to say that they use it for something like "non-blocking
  testing" while developing in a local machine}, and \emailsD{} of
developers who provided an alternative answer (option ``d'') mentioned
that using parallelism was not worth the effort of preparing the test
suites to take advantage of available processing power.  A total of
\emailsNA{} of participants did not answer the last question of the
survey.  Figure~\ref{fig:rq5-answers} shows a pie chart summarizing
the distribution of answers.
